
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Ans Khan} % Your name
% You can merge both of these into a single line, if you do not have a website.
% \address{+92 3177148611 \\ Multan, PK} 
\address{\href{mailto:the.ans.khan@gmail.com}{the.ans.khan@gmail.com} \\
\href{https://anskhan.netlify.app}{anskhan.netlify.app} \\  
\href{https://github.com/Muhammad-AnasKhan/}{github.com/Muhammad-AnasKhan/}\\	 \href{https://www.linkedin.com/in/muhammad-ans-khan/}{/in/muhammad-ans-khan}}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}%{OBJECTIVE}

{Fresh Graduate - Software Engineer with over 3 years (including undergraduate) of experience in Full Stack Web and Mobile App Development, AI Enthusiast.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
%Relevant Coursework: A, B, C, and D.

{\bf Bachelor of Information Technology}, University of Education - {\bf 3.6/4.0 }\hfill {2020 - 2024} 
\\
{\bf Fsc  - Pre Engineering}, City College Multan - 88\% \hfill {2018 - 2020}
\\
{\bf Matric}, Govt. Comprehensive Higher Secondary School - 88\% \hfill {2016 - 2018}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\textbf{Technical Skills:}
\begin{itemize}
	\item \textbf{Full Stack Development}: Django, PHP, ASP.NET Core, Node.js, React, MERN Stack, Rest API's
	\item \textbf{Mobile Development}: Android, Flutter
	\item \textbf{Databases}: MySQL, MS SQL, PostgreSQL, MongoDB, Firebase, SQLite, ORMs
	\item \textbf{Version Control}: Git, GitHub, Bit bucket, GitLab
	\item \textbf{Cloud Services, Containerization \& Deployment}: AWS, MS Azure, Docker, Linux
%	\item \textbf{Containerization \& Deployment}: 
	\item \textbf{Debugging and Troubleshooting}
	
\end{itemize}


\textbf{Soft Skills:} 
\begin{itemize}
\item Rapid Learner, Problem Solver, Team Collaboration, Effective Communication
\end{itemize}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical Skills & Problem Solving, Full Stack Development\\
%Soft Skills: & Quick Learning, Problem Solving, Collaboration, Communication\\
%\end{tabular}

\end{rSection}
  
\begin{rSection}{EXPERIENCE}

\textbf{Full Stack Development} \hfill 2022 - Present\\
Freelance/Remote % \hfill \textit{San Francisco, CA}
 \begin{itemize}
    \itemsep -3pt {} 
    % \item Got opportunity to work with multiple diverse tech stacks
     \item Architected and maintained full stack applications with varied tech stacks including using Django, PHP, ASP.NET Core, Node.js, and the MERN Stack.
     % including Django, PHP, ASP.NET Core, Node JS, MERN Stack
     \item Developed mobile applications using Android and Flutter
     \item Managed databases including MySQL, MS SQL, PostgreSQL, MongoDB, Firebase, and SQLite. \item Utilized version control systems like Git, GitHub, Bitbucket, and GitLab.
     \item Deployed apps on AWS and MS Azure with Docker on Linux, debugging systems 
 \end{itemize}


\textbf{Front-end Development} \hfill 2021  - Present\\
Freelance/Remote  \hfill %\textit{San Francisco, CA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Gained expertise in core web technologies, detailed at  \href{https://anskhan.netlify.app/projects}{https://anskhan.netlify.app/projects}
     \item Created websites using HTML, CSS, JavaScript, Bootstrap, jQuery, and WordPress.
   
 \end{itemize}
 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Personal Portfolio Website}  - \href{https://anskhan.netlify.app}{https://anskhan.netlify.app}
%\item   {- Crafted this portfolio website for showcasing my projects.}
\item \textbf{Automated University TimeTable Scheduler - Django}

\iffalse

% follwing is the multi line comment followed by \iffalse

 {Built a tool to easify the hectic and stressfull process of organization timetabling. Problem needed to solve was to make the process distributed instead of the current centralised timetable scheduling process. Keeping provided features for admin and teachers to solve the problem and create personalized timetables. Implemented two ways to get the final scheduled timetable, i.e. Randomised and personalized timetables}
 
\fi
 
 \begin{itemize}
 	\item Engineered a tool using Django(Python's Web Framework) to automate and decentralize university timetabling.
 	\item Addressed inefficiencies by shifting from centralized to distributed scheduling.
 	\item Implemented secure user authentication and authorization, with role-based access control for administrators and teachers.
 	\item Designed and integrated features for administrators and teachers to create personalized timetables.
 	\item Implemented two scheduling methods:
 	\begin{itemize}
 		\item \textbf{Randomized Scheduling:} Auto-generates timetables without specific preferences.
 		\item \textbf{Personalized Scheduling:} Customizes timetables based on user preferences.
 	\end{itemize}
 	\item Reduced timetable creation time and effort, enhancing user satisfaction and organizational efficiency.
 	\item Technologies: Django, Python, Django ORM, PyCharm, VS Code, MS SQL server, JavaScript, jQuery, HTML, CSS.
 \end{itemize}
 
 \item \textbf{Fuel Station Information System - ASP.NET Core MVC}
 
  \begin{itemize}
 	\item Developed a comprehensive web-based application using ASP.NET Core MVC to manage and track fuel station operations.
 	\item Optimized fuel inventory management by allowing real-time tracking.
 	\item Implemented reporting and analytics to visualize data with charts and graphs, enabling better decision-making.
 
 	\item Implemented secure user authentication and authorization, with role-based access control for Admin, Manager, and Staff.
 	\item Technologies: C Sharp, ASP.NET Core MVC, Razor Pages, OOP, SQL, Microsoft SQL Server, HTML5, CSS3, JavaScript, Bootstrap, Javascript Charts.
 \end{itemize}
 
\item \textbf{Navigation App - Flutter} 
 \begin{itemize}
\item {Engineered a mobile app helping to navigate through map(pre loaded) fully offline. Utilized socket server with embedded sensors to obtain coordinates, speed and other meta data.}
\item {Technologies: Flutter, Dart}
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
	\textbf{Technical Domain - NFTP} \hfill 2021 
    \item {Full Stack Web App Development Training - Punjab Information Technology
    Board}



\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
