
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Ans Khan} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{tel:+92 3177148611}{+92 3177148611}  \\ Multan, Pakistan} 
\address{\href{mailto:the.ans.khan@gmail.com}{the.ans.khan@gmail.com} \\
\href{https://anskhan.netlify.app}{anskhan.netlify.app} \\  
\href{https://github.com/Muhammad-AnasKhan/}{github.com/Muhammad-AnasKhan/}\\	 \href{https://www.linkedin.com/in/muhammad-ans-khan/}{/in/muhammad-ans-khan}}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}%{OBJECTIVE}

{Software Engineer with 3+ years of experience in Full Stack Web and Mobile App Development, with expertise in developing and deploying scalable applications on cloud platforms.}


\end{rSection}


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\textbf{Technical Skills:}
\begin{itemize}
	\item \textbf{Frontend}: Html, Css, JS, Bootstrap, jQuery, ajax, Tailwind, React, Angular
	\item \textbf{Backend}:  Django, .NET, .NET Core, Rest API's
	\item \textbf{Databases}: MySQL, MS SQL Server, PostgreSQL, MongoDB, Firebase, SQLite, ORMs, EfCore
	\item \textbf{Mobile Development}: Android, Flutter
	\item \textbf{Version Control}: Git, GitHub, Bit bucket, GitLab
	\item \textbf{Cloud Services, Containerization \& Deployment}: AWS, MS Azure, Docker, Linux
%	\item \textbf{Containerization \& Deployment}: 
	\item \textbf{Integrations}: Stripe, Google Auth, Twillio
	\item \textbf{Debugging and Troubleshooting}
	
\end{itemize}


\textbf{Soft Skills:} 
\begin{itemize}
\item Rapid Learner, Problem Solver, Team Collaboration, Effective Communication
\end{itemize}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical Skills & Problem Solving, Full Stack Development\\
%Soft Skills: & Quick Learning, Problem Solving, Collaboration, Communication\\
%\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{EXPERIENCE}
	
	\textbf{Software Engineer} \hfill 2024 - Present\\
	Atrule Technologies - Onsite % \hfill \textit{San Francisco, CA}
	\begin{itemize}
		\itemsep -3pt {} 
		\item Contributed in revamping legacy ASP pages application to .NET web forms increasing application performance and load times.
		\item Build and deployed services using .NET core, Azure Functions and Azure Services Bus Queues.
		\item Worked with ASP, ASP.NET Core, Web APIs, Web Forms, MS SQL Server, Ms Azure.
		
		% including Django, PHP, ASP.NET Core, Node JS, MERN Stack
		\item Developed web scraping scripts using Python to get products images by name.
		\item Utilized version control systems like Git, GitHub for code collaboration and to keep sync with teams.
		
		\textbf{Key Projects at Atrule Technologies:}
		\begin{itemize}
			\itemsep -3pt {} 
			\item \textbf {Wynshop Customer Notification App} 
			\begin{itemize}
				\itemsep -3pt {} 
				\item Built a comprehensive customer notification application backend using .NET Core Web API to manage order processing, user authentication, and notifications.
				\item Integrated role-based authentication for secure access control across different user roles.
				\item Leveraged Twilio integration for SMS notifications, including URL shortening for efficient, user-friendly messages.
				\item Applied CQRS (Command Query Responsibility Segregation) to streamline the command handling and query processes, optimizing system scalability and performance.
				\item Technologies: .NET Core Web API, Twilio, CQRS, Role-Based Authentication, URL Shortening, C\#, React Js
			\end{itemize}
			\item \textbf {Automated Background Job Scheduling Service} 
			\begin{itemize}
				\itemsep -3pt {} 
				\item Developed a robust background job scheduling service utilizing Quartz.NET, .NET Core Web API, Azure Functions, and Azure Queues to handle high-frequency automated tasks.
				\item Designed and implemented a dashboard for managing scheduled jobs, allowing real-time monitoring, creation, and updates of tasks.
				\item Configured cron expression triggers for flexible scheduling, ensuring precise job execution timing based on business requirements.
			\end{itemize}
		\end{itemize}
		
	\end{itemize}
	\textbf{Software Engineer} \hfill 2022 - 2024\\
	Algosden Solutions -  \href{https://www.algosden.com/}{algosden.com}
		\begin{itemize}
		\itemsep -3pt {} 
		% \item Got opportunity to work with multiple diverse tech stacks
		\item Architected, developed and deployed full stack applications using Django, .NET, .NET Core, SQL server, SSRS.
		\item Worked on complex and functional applications using ASP.NET Core MVC, razor pages, CSS, JavaScript, Bootstrap, jQuery, Javascript charts.
		
		\textbf{Key Projects at Algosden:}
			\begin{itemize}
			\itemsep -3pt {} 
			\item \textbf{2do.us - Django/Python}
			
				\begin{itemize}
					\itemsep -3pt {} 
					\item Developed and deployed a comprehensive web-based application with using Django to manage tasks, tickets, communities, teams, invoices, reporting, etc.
					\item Implemented Stripe payment gateway with robust invoicing management.
					
					\item Implemented secure user authentication and authorization, with role-based access control for Admin, Manager, and User.
					\item Technologies: Python, Django, OOP, SQL,Postgres, HTML5, CSS3, JavaScript, Bootstrap, Stripe, jQuery.
				\end{itemize}
			\end{itemize}
		\begin{itemize}
			\itemsep -3pt {} 
			\item \textbf{Fuel Station Information System}
			
			\begin{itemize}
				\itemsep -3pt {} 
				\item Developed and deployed a comprehensive web-based application with 20,000+ lines of code using ASP.NET Core MVC to manage and track fuel station operations.
				\item Implemented reporting and analytics to visualize data with charts and graphs, enabling better decision-making.
				
				\item Implemented secure user authentication and authorization, with role-based access control for Admin, Manager, and Staff.
				\item Technologies: C Sharp, ASP.NET Core MVC, Razor Pages, OOP, SQL, Microsoft SQL Server, HTML5, CSS3, JavaScript, Bootstrap, Javascript Charts.
			\end{itemize}
		\end{itemize}
	
		 
	\end{itemize}
	
	\textbf{Full Stack Engineer} \hfill 2022 - 2024\\
	Freelance/Remote % \hfill \textit{San Francisco, CA}
	\begin{itemize}
		\itemsep -3pt {} 
		% \item Got opportunity to work with multiple diverse tech stacks
		\item Architected, developed and deployed full stack applications with varied tech stacks including using .NET, Django, php, Node.js.
		% including Django, PHP, ASP.NET Core, Node JS, MERN Stack
		\item Developed mobile applications using Android and Flutter
		\item Managed and optimized databases including MySQL, MS SQL, PostgreSQL, MongoDB, Firebase, and SQLite for integrity and performance. 
		\item Utilized Git, GitHub, Bitbucket, and GitLab for streamlined collaboration and code management.
		\item Utilized the superpower of AWS and MS Azure for deploying scalable applications.
	\end{itemize}
	
	
	\textbf{Front-end Engineer} \hfill 2021  - 2023\\
	Freelance/Remote  \hfill %\textit{San Francisco, CA}
	\begin{itemize}
		\itemsep -3pt {} 
		\item Developed proficiency in core web technologies, transforming UI designs into dynamic HTML templates.
		\item Built responsive websites using HTML, CSS, JavaScript, Bootstrap, jQuery, and WordPress. \\
		
	\end{itemize}
	
	
	
	%----------------------------------------------------------------------------------------
	%	Project SECTION
	%----------------------------------------------------------------------------------------

  
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Personal Portfolio Website}  - \href{https://anskhan.netlify.app}{https://anskhan.netlify.app}
%\item   {- Crafted this portfolio website for showcasing my projects.}



	\item \textbf{2do.us - Django/Python}
	
	\begin{itemize}
		\itemsep -3pt {} 
		\item Developed and deployed a comprehensive web-based application with using Django to manage tasks, tickets, communities, teams, invoices, reporting, etc.
		\item Implemented Stripe payment gateway with robust invoicing management.
		
		\item Implemented secure user authentication and authorization, with role-based access control for Admin, Manager, and User.
		\item Technologies: Python, Django, OOP, SQL,Postgres, HTML5, CSS3, JavaScript, Bootstrap, Stripe, jQuery.
	\end{itemize}


\item \textbf{Fuel Station Information System - ASP.NET Core MVC}

\begin{itemize}
	\item Developed and deployed a comprehensive web-based application with 20,000+ lines of code using ASP.NET Core MVC to manage and track fuel station operations.
	\item Implemented reporting and analytics to visualize data with charts and graphs, enabling better decision-making.
	
	\item Implemented secure user authentication and authorization, with role-based access control for Admin, Manager, and Staff.
	\item Technologies: C Sharp, ASP.NET Core MVC, Razor Pages, OOP, SQL, Microsoft SQL Server, HTML5, CSS3, JavaScript, Bootstrap, Javascript Charts.
\end{itemize}

\item \textbf{Full Stack - Party Invites App - .NET Core}
\begin{itemize}
	\item Developed a web-based Party Invites App using .NET Core to  manage, and track party invitations and RSVPs.
	\item Integrated secure user authentication and authorization using ASP.NET Core.
	\item Implemented responsive UI with ASP.NET Core MVC, Razor Pages, Bootstrap, and jQuery for seamless user experience across devices.
	
	\item Deployed to Microsoft Azure with Azure App Service and Azure SQL Database.
	\item Technologies: C Sharp, ASP.NET Core MVC, Razor Pages, OOP, SQL, Microsoft SQL Server, HTML5, CSS3, JavaScript, Bootstrap.
\end{itemize}



\item \textbf{Automated University TimeTable Scheduler - Django}

\iffalse

% follwing is the multi line comment followed by \iffalse

 {Built a tool to easify the hectic and stressfull process of organization timetabling. Problem needed to solve was to make the process distributed instead of the current centralised timetable scheduling process. Keeping provided features for admin and teachers to solve the problem and create personalized timetables. Implemented two ways to get the final scheduled timetable, i.e. Randomised and personalized timetables}
 
\fi
 
 \begin{itemize}
 	\item Engineered a tool using Django(Python's Web Framework) to automate and decentralize university timetabling.
 	\item Addressed inefficiencies by shifting from centralized to distributed scheduling.
 	\item Implemented secure user authentication and authorization, with role-based access control for administrators and teachers.
 	\item Designed and integrated features for administrators and teachers to create personalized timetables.
 	\item Implemented two scheduling methods:
 	\begin{itemize}
 		\item \textbf{Randomized Scheduling:} Auto-generates timetables without specific preferences.
 		\item \textbf{Personalized Scheduling:} Customizes timetables based on user preferences.
 	\end{itemize}
 	\item Reduced timetable creation time and effort, enhancing user satisfaction and organizational efficiency.
 	\item Technologies: Django, Python, Django ORM, PyCharm, VS Code, MS SQL server, JavaScript, jQuery, HTML, CSS.
 \end{itemize}

\end{rSection} 
\end{rSection} 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
	%Relevant Coursework: A, B, C, and D.
	
	{\bf Bachelor of Information Technology}, University of Education - {\bf 3.6/4.0 }\hfill {2020 - 2024} 
	\\
	{\bf Fsc  - Pre Engineering}, City College Multan - 88\% \hfill {2018 - 2020}
	\\
	{\bf Matric}, Govt. Comprehensive Higher Secondary School - 88\% \hfill {2016 - 2018}
	%Minor in Linguistics \smallskip \\
	%Member of Eta Kappa Nu \\
	%Member of Upsilon Pi Epsilon \\
	
	
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
	\textbf{Technical Domain - NFTP} \hfill 2021 
    \item {Full Stack Web App Development Training - Punjab Information Technology
    Board}



\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
