\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Ans Khan} % Your name
% You can merge both of these into a single line, if you do not have a website.
% \address{+92 3177148611 \\ Multan, PK} 
\address{\href{mailto:the.ans.khan@gmail.com}{the.ans.khan@gmail.com} \\
\href{https://anskhan.netlify.app}{anskhan.netlify.app} \\  
\href{https://github.com/Muhammad-AnasKhan/}{github.com/Muhammad-AnasKhan/}\\	 \href{https://www.linkedin.com/in/muhammad-ans-khan/}{/in/muhammad-ans-khan}}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}%{OBJECTIVE}

{Fresh Graduate - Software Engineer with over 3 years (including undergraduate) of experience in Full Stack Web and Mobile App Development}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
%Relevant Coursework: A, B, C, and D.

{\bf Bachelor in Information Technology}, University of Education \hfill {2020 - 2024} 
\\
{\bf Fsc  - Pre Engineering}, City College Multan \hfill {2018 - 2020}
\\
{\bf Matric}, Govt. Comprehensive Higher Secondary School \hfill {2016 - 2018}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\textbf{Technical Skills:}
\begin{itemize}
	\item \textbf{Full Stack Development}: Python, Data Analysis, datasets, Jupyter Notebooks, Django, PHP, ASP.NET Core, MERN Stack, Rest API's
	\item \textbf{Mobile Development}: Android, Flutter
	\item \textbf{Databases}: MySQL, MS SQL, PostgreSQL, MongoDB, Firebase, SQLite
	\item \textbf{Version Control}: Git, GitHub, Bitbucket, GitLab
	\item \textbf{Cloud Services, Containerization \& Deployment}: AWS, MS Azure, Docker, Linux
%	\item \textbf{Containerization \& Deployment}: 
	\item \textbf{Debugging and Troubleshooting}
	\item Ability to handle intermediate-level Python coding tasks and understand algorithmic concepts.
	\item Strong problem-solving skills, complemented by exceptional reasoning and mathematical abilities.
	\item {Proficiency in Python programming language for coding and debugging.}
\end{itemize}
\textbf{Soft Skills:} Quick Learning, Problem Solving, Collaboration, Proficient in English, Communication

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical Skills & Problem Solving, Full Stack Development\\
%Soft Skills: & Quick Learning, Problem Solving, Collaboration, Communication\\
%\end{tabular}

\end{rSection}
  
\begin{rSection}{EXPERIENCE}

\textbf{Full Stack Development} \hfill 2022 - Present\\
Freelance/Remote % \hfill \textit{San Francisco, CA}
 \begin{itemize}
    \itemsep -3pt {} 
    % \item Got opportunity to work with multiple diverse tech stacks
     \item Built and maintained full stack applications with multiple diverse tech stacks including python.
     % including Django, PHP, ASP.NET Core, Node JS, MERN Stack
     \item Developed mobile apps (Android, Flutter), managed databases (MySQL, MS SQL, PostgreSQL, MongoDB, Firebase, SQLite), and used version control (Git, GitHub, Bitbucket, GitLab).
     \item Deployed apps on AWS and MS Azure with Docker on Linux, debugging systems 
 \end{itemize}



\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Personal Portfolio Website}  - \href{https://anskhan.netlify.app}{https://anskhan.netlify.app}
%\item   {- Crafted this portfolio website for showcasing my projects.}
\item \textbf{Automated University TimeTable Scheduler - Django} {Built a tool to easify the hectic and stressfull process of organization timetabling. Approach is to make the process distributed instead of the current centralised timetable scheduling.}
%\item \textbf{Navigation App - Flutter} {Build a mobile app helping to navigate through map(pre loaded) fully offline.}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
	\textbf{Technical Domain - NFTP} \hfill 2021 
    \item {Full Stack Web App Development Training - Punjab Information Technology
    Board}



\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
