
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muhammad Ans Khan} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{tel:+92 3177148611}{+92 3177148611}  \\ Multan, Pakistan} 
\address{\href{mailto:the.ans.khan@gmail.com}{the.ans.khan@gmail.com} \\
\href{https://anskhan.netlify.app}{anskhan.netlify.app} \\  
\href{https://github.com/Muhammad-AnasKhan/}{github.com/Muhammad-AnasKhan/}\\	 \href{https://www.linkedin.com/in/muhammad-ans-khan/}{/in/muhammad-ans-khan}}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}%{OBJECTIVE}

{Software Engineer with 3+ years of experience in Full Stack Development, specializing in .NET and modern web technologies. Proven ability to design scalable applications, integrate advanced APIs, and leverage cloud platforms for robust solutions. %Skilled in building scalable solutions, API integrations, and optimizing workflows for performance.
}


\end{rSection}


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\textbf{Technical Skills:}
\begin{itemize}
	\item \textbf{Frontend}: HTML, CSS, JS, Bootstrap, jQuery, Ajax, Tailwind, React, Angular
	\item \textbf{Backend}:  .NET, .NET Core, Rest API's, Django
	\item \textbf{Databases}: SQL Server, PostgreSQL, MongoDB, MySQL, SQLite, ORMs, EfCore
	\item \textbf{Mobile Development}: (Familar): Android, Flutter
	\item \textbf{Tools}: Git, GitHub, Bit bucket, GitLab, Azure DevOps, Postman, Swagger
	\item \textbf{Cloud}: AWS, Azure, Docker, Linux
%	\item \textbf{Containerization \& Deployment}: 
	\item \textbf{Integrations}: Stripe, Twillio, MS Graph, MS Teams, OAuth 2.0, SSO, Webhooks
%	\item \textbf{Debugging and Troubleshooting}
	
\end{itemize}


\textbf{Soft Skills:} 
\begin{itemize}
\item Rapid Learner, Problem Solver, Team Collaboration, Effective Communication
\end{itemize}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Technical Skills & Problem Solving, Full Stack Development\\
%Soft Skills: & Quick Learning, Problem Solving, Collaboration, Communication\\
%\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{EXPERIENCE}
	
	\textbf{Software Engineer} \hfill June 2024 - Present\\
	Atrule Technologies - Onsite % \hfill \textit{San Francisco, CA}
	%\begin{itemize}
		\itemsep 1pt {} 
				
		\item - Developed and optimized scalable web solutions by revamping legacy systems, building robust backends with .NET and Azure services, automating workflows, ensuring performance and efficiency.
		
	%	\item Built scalable backend services with .NET Core, Azure Functions, Service Bus, MS Graph, MS Teams, and Twilio for robust functionality.
		
		\textbf{Key Projects:}
		\begin{itemize}
			\itemsep -5pt {} 
			\item \textbf {Skeddle LMS App} 
			\begin{itemize}
				\itemsep -5pt {} 
				\item Contributed to the integration of MS Teams API for event and webinar management, leveraging Graph API and OAuth 2.0 for seamless authentication and data synchronization.
				\item Technologies: Angular, .NET Core Web API, MS Teams API, Graph API, OAuth 2.0, C\#.
			\end{itemize}
			\item \textbf {Wynshop Customer Notification App} 
			\begin{itemize}
				\itemsep -5pt {} 
				\item Built a .NET Core Web API backend supporting secure role-based authentication, order management, and Twilio-powered SMS notifications with URL shortening.
				\item Technologies: .NET Core Web API, Twilio, CQRS, Role-Based Authentication, Rebrandly URL Shortening, C\#, React Js
			\end{itemize}
			\item \textbf {Automated Job Scheduling Service} 
			\begin{itemize}
				\itemsep -5pt {} 
				\item Engineered a job scheduling system using Quartz.NET, Azure Functions, and Queues, with a dashboard for job management and cron-based scheduling.			
				\item Technologies: Quartz.NET, .NET Core, Azure Functions, Azure Queues, Cron Expressions, C\#.  \\ \\ \\ \\
			\end{itemize}
		\end{itemize}
		
	%\end{itemize}
	
	\textbf{.NET Engineer} \hfill Jan 2022 - June 2024\\
	Algosden Solutions -  \href{https://www.algosden.com/}{algosden.com}
	%\begin{itemize}
		\itemsep 1pt {} 
		% \item Got opportunity to work with multiple diverse tech stacks
		\item - Designed, developed, and deployed full-stack web applications using ASP.NET Core and modern front-end technologies like Razor Pages, JavaScript, and Bootstrap. 
		
		\item 
		\textbf{Key Projects:}
		\begin{itemize}
			\itemsep -3pt {} 
			\item \textbf{Fuel Station Information System}
			
			\begin{itemize}
				\itemsep -3pt {} 
				\item Developed and deployed a comprehensive web solution using ASP.NET Core MVC to manage fuel station operations with secure role-based authentication, reporting and analytics charts enabling better decision-making.

				\item Technologies: .NET Core MVC, Razor Pages, OOP, C\#, SQL Server, HTML5, CSS3, JavaScript, Bootstrap, JavaScript Charts.
			\end{itemize}
		\end{itemize}
	
		 
	%\end{itemize}
	
	\textbf{Full Stack Engineer} \hfill 2022 - 2024\\
	Freelance/Remote % \hfill \textit{San Francisco, CA}
	\begin{itemize}
		\itemsep -3pt {} 
		% \item Got opportunity to work with multiple diverse tech stacks
		\item Designed and developed full-stack applications using diverse technologies, including .NET, Django, PHP, and Node.js.
		\item Created mobile applications with Android and Flutter
	\end{itemize}
	
	
	\textbf{Front-end Engineer} \hfill 2021  - 2023\\
	Freelance/Remote  \hfill %\textit{San Francisco, CA}
	\begin{itemize}
		\itemsep -3pt {} 
		\item Translated UI designs into dynamic and responsive websites using HTML, CSS, JavaScript, Bootstrap, and jQuery.
		
		\item Built and customized websites on WordPress, ensuring functionality and optimal user experience. \\
		
	\end{itemize}
	
	
	
	%----------------------------------------------------------------------------------------
	%	Project SECTION
	%----------------------------------------------------------------------------------------

  
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Personal Portfolio Website}  - \href{https://anskhan.netlify.app}{https://anskhan.netlify.app}
%\item   {- Crafted this portfolio website for showcasing my projects.}

\item \textbf{Party Invites App - .NET Core}
\begin{itemize}
	\item Developed a web app to manage party invitations and RSVPs with responsive UI and secure authentication.
	\item Deployed to Microsoft Azure with Azure App Service and Azure SQL Database.
	\item Technologies: .NET Core MVC, Razor Pages, SQL Server, C\#, Bootstrap.
\end{itemize}

% follwing is the multi line comment followed by \iffalse
\iffalse
\item \textbf{Automated University TimeTable Scheduler - Django}





 {Built a tool to easify the hectic and stressfull process of organization timetabling. Problem needed to solve was to make the process distributed instead of the current centralised timetable scheduling process. Keeping provided features for admin and teachers to solve the problem and create personalized timetables. Implemented two ways to get the final scheduled timetable, i.e. Randomised and personalized timetables}

 
 \begin{itemize}
 	\item Developed a tool using Django to decentralize timetabling, reducing timetable creation time and effort, enhancing organizational efficiency.
 	\item Designed and integrated features for administrators and teachers to create personalized timetables.
 	\item Implemented two scheduling methods:
 	\begin{itemize}
 		\item \textbf{Randomized Scheduling:} Auto-generates timetables without specific preferences.
 		\item \textbf{Personalized Scheduling:} Customizes timetables based on user preferences.
 	\end{itemize}

 	\item Technologies: Django, Python, Django ORM, PyCharm, VS Code, MS SQL server, JavaScript, jQuery, HTML, CSS.
 \end{itemize}
\fi
\end{rSection} 
\end{rSection} 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
	%Relevant Coursework: A, B, C, and D.
	
	{\bf Bachelor of Information Technology}, University of Education - {\bf 3.6/4.0 }\hfill {2020 - 2024} 
	\\
	{\bf Fsc  - Pre Engineering}, City College Multan - 88\% \hfill {2018 - 2020}
	\\
	{\bf Matric}, Govt. Comprehensive Higher Secondary School - 88\% \hfill {2016 - 2018}
	%Minor in Linguistics \smallskip \\
	%Member of Eta Kappa Nu \\
	%Member of Upsilon Pi Epsilon \\
	
	
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
	\textbf{Technical Domain - NFTP} \hfill 2021 
    \item {Full Stack Web App Development Training - Punjab Information Technology
    Board}



\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
